Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-05-31 prevalence_testing/postshocktest2022draft.tex
edited manuscript

\textcolor{red}{This needs work} The core idea of our methodology is to first form a donor pool of time series that have undergone similar shocks, then perform the multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi}  with respect to each of these donors to determine whether the shock is prevalent or transient, and then aggregate the decisions from the donors to make a final decision of transience or prevalence for the time series under study for which no post-shock observations are observed. The multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi} is a natural  extension of \cite{diebold1995comparing}. The post-shock setting follows similar logic as that in \cite{lin2021minimizing}.
%Our testing method embraces ideas from forecast aggregation in the post-shock setting \citep{lin2021minimizing}, forecast comparison \citep{diebold1995comparing, quaedvlieg2021multi}, and p-value combination. 
Our procedure has conceptual similarities with 
conditional forecasting \citep{baumeister2014real, kilian2017structural}, 
time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, 
forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, 
synthetic control methodology \citep{abadie2010synthetic}, 
synthetic interventions \citep{agarwal2020synthetic, agarwal2020two}, 
and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}. The synthetic intervention approach in \cite{agarwal2020two} is particularly relevant to our method. These authors construct a panel of countries undergoing a variety of interventions and use it to estimate what COVID case trajectories for a particular country would have looked like under different chosen courses of action. They then demonstrate that the method well replicates the observed trajectories of countries under the chosen intervention. This method works well because there are multiple countries undergoing similar interventions in response to a common shock which occurs at a similar past time for each country. In our setting, we do not specify that the time series in the donor pool be temporally similar to the time series under study, but we require that the shocks to those time series be similar to the shock of the time series under study. In \cite{lin2021minimizing} this similarity was stated in the form of a shock-effect distribution. In the present work, we parameterize similarity into post-shock dynamics for an autoregressive process.

As alluded to above, the success of our approach hinges on the construction of a suitable donor pool that possess similar post-shock dynamics to the time series under study. We develop a pragmatic parametric time series model which parameterizes such a structure. Without such a parameterization there is no avenue for connecting decisions made regarding the post-shock information in the donor pool with the yet-to-be observed post-shock information corresponding to the time series under study. The parameterization that we use states that the post-shock dynamics are determined in part by observed covariates collected right before the first post-shock response is observed. Such a parameterization will not be known in practice. That being said, one can demonstrate the effectiveness and appropriateness of such a parameterization via a leave one out cross validation approach applied to the donor pool in which all post-shock information is observed \textcolor{red}{need LOOCV approach}. A similar prospective approach was discussed in \cite{lin2021minimizing}. We demonstrate the utility of our prevalence testing approach on two real data examples forecasting daily Conoco Phillips stock prices and monthly employment data as well as several simulation examples. Our simulation examples show settings in which our method is expected to work well and demonstrate that the appropriateness of the method decreases as the parametric specifications break down. In the real data examples, we show that the decisions obtained from the donor pool match those that would be observed in the future.

@@

In this section we discuss the background of the multi-horizon forecasting procedure \citep{quaedvlieg2021multi} that is necessary for the investigation of shock behavior in our anticipated post-shock setting. The initial building blocks in the assessment of predictive ability of forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ will make use of a loss differential
$$
  \dbf_{i,t} =  \textcolor{red}{\Llet_{i,t,2} - \Llet_{i,t,1}},
$$
where $\Llet_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function. Define the expected loss differential as  $E(\dbf_{i,t}) = \mbf\mu_{i,t}$ and let the average expected loss differential be defined as $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
%Hypothesis tests in \cite{quaedvlieg2021multi} are then constructed with respect to estimates of the expected loss differentials $E(\dbf_{i,t}) = \mbf\mu_{i,t}$, %Conditions for these tests require conditions of \cite{giacomini2006tests}. 
%where specific interest is in the average expected loss differential $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
%%%\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$. We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock. Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool. 
%%%\vspace*{0.5cm}
We will then judge forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ based on the average superior predictive ability (aSPA) \citep{quaedvlieg2021multi}. The aSPA investigates forecast comparisons based on their weighted average loss difference
$$
  \mu^{(\text{Avg})}_i = \textbf{w}_i'\mathbf{\mu}_i = \sum_{h=1}^H w_{i,h} \mu_i^h,
$$
with weights $\textbf{w}_i$ that sum to one. Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu_i^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1. With this caveat in mind we will use $w_{i,h} = 1/H$, and we will consider different time horizons $H$ in some of our examples.

\textcolor{red}{Define $\mbf{D}_i = (\mbf{d}_{i, T^*_i+H+1}', \ldots, \mbf{d}_{i, T_i}')$, which is the loss differential matrix of $i$th time series. Note that $\mbf{D}_i$ is of dimension $T_i-T^*_i - H$.   $\mbf{D}_i$ compares $h$-step forecasts of $y_{i, t}$ for $t = T^* + H + 1$ to $t = T$ and $h= 1, \ldots, H$. In this design, adjusted and unadjusted forecasts are different with probability one such that elements of $\mbf{D}_i$ are different from zero with probability one. This prevents excessive zeroes to affect our inference results if $t = H+K +1,  \ldots, T$, where $K$ is the training sample size for parameter estimation of $h$-step forecasts.}

@@

%We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = l\textcolor{red}{U_i}$. Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array 
$$
  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
$$
The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.

\begin{equation} \label{whb}
	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{\textcolor{red}{U_i}}\sum_{k=1}^{\textcolor{red}{U_i}}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
\end{equation}
where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
\begin{equation} \label{boott}
  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
  \Big\vert \overset{P}{\longrightarrow} 0,
\end{equation}
as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
\begin{equation} \label{bootp}
  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
\end{equation}
The results \eqref{boott} implies that 
$$
  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
$$
where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$. Therefore bootstrap inference in the donor pool is a good approximation. %We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.

@@

The first approach is a weighted average of the p-values computed in the donor pool which are calculated as in Section \ref{sec:multhor}. The weights reflect the similarity between $\x_{i,T^*_i+1}$ and $\x_{1,T^*_1+1}$, and are similar to the weights computed in \cite{lin2021minimizing}. We now discuss the details. Let
\begin{align*}
	\bs{X}= \begin{pmatrix}
		\bs{x}_{1, T_1^*+1}  \\
		\vdots   \\
		\bs{x}_{n+1, T_{n+1}^*+1} 
	\end{pmatrix}.
\end{align*}
\textcolor{red}{In this paper, we consider this simple form of $\bs{X}$ for illustrative purpose. However,  more general $\bs{X}$'s are allowable. For example, $\bs{X}$ can also include $\bs{x}_{i, T_i^*-j+1}$ for $j = 2, \ldots, q_2$, which considers the lagged covariates in the dynamic model \eqref{model-gen}.} Let $\bs{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1. We compute the weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}. Note that the modeling part for the response $y_{i,t}$ does not necessarily involve scaled covariates. From this construction we obtain the weighted average p-value 
\begin{equation} \label{wpval}
 \hat{p}_1 = \sum_{i=2}^{n+1} w_i^* \hat{p}_i^B,	
\end{equation}
where $\hat{p}_i^B$ is given as \eqref{bootp} and $w_i^*$ is the weight corresponding to the similarity between the first and $(i+1)$th row of $\mbf{X}^*$.

We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool. \textcolor{red}{Given a significance level $\alpha$ and estimates $\{\hat{p}_i^B \colon i = 2, \ldots, n+1\}$, we compute the vote}
\begin{align*}
	V = I\Big\{\frac{1}{n} \sum_{i=2}^{n+1} I (\hat{p}_i^B\leq \alpha) \geq 0.5\Big\},
\end{align*}
\textcolor{red}{where $I(\cdot)$ is an indicator function. The idea of voting is very intuitive in the sense that donors vote for the shock persistence or transience  using a hypothesis testing approach and the one receiving more votes is returned.  Second, the weighted voting generalizes this idea by making using of  the similarity weights $\mbf{W}^*$. It is defined as }
\begin{align*}
	V^* = I\Big\{ \sum_{i=2}^{n+1} w_i^* I (\hat{p}_i^B\leq \alpha) \geq 0.5\Big\}.
\end{align*}

\textcolor{red}{Algorithm \ref{Bu} describes the mechanics of computing $\mbf{W}^*, \hat{p}_1, V, V^*$ in more detail. There are a couple of details that are worth noting. First, for $t = T_i+1$ and $i \geq 2$, we used to the methodology of \cite{lin2021minimizing} to compute point forecast for $\hat{y}_{i,t}^{2,h}$. Note that for $t = T_i+1$, using ordinary least square conditional forecast yields $\hat{y}_{i,t}^{2,h}=  \hat{y}_{i,t}^{1,h}$ as those two forecast just differ by shock information, which is not available at this time point. We make such adjustment for the reason that  the method of  \cite{lin2021minimizing} is generally more likely to perform better than the ordinary forecast under certain conditions. Second, notice that we evaluate forecast comparison for $t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$ with time length smaller than $T_i$. It is because the framework of \cite{quaedvlieg2021multi} needs training sample, which implicitly requires users to feed the algorithm with moderately large dataset for a more credible analysis. }

@@

 		\If{$t-h = T_i^*$, $i\geq 3$, and $h =1$}{
 		$\hat{y}_{i,t}^{2, h}= \hat{y}_{i,t}^{2, h} + \hat{\alpha}_{\rm wadj}$
 		}
 		Compute the squared error loss \textcolor{red}{$l_{i,t,h, 1}$} based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{1, h}$\\
 		 Compute the squared error loss \textcolor{red}{$l_{i,t,h, 2}$} based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{2, h}$
 		}
 	}
 	Construct the loss differential matrix   with element \textcolor{red}{$l_{i,t,h, 2}-l_{i,t,h, 1}$} at $t$th row and $h$th column \\
 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix \textcolor{red}{$\{l_{i,t,h,2}-l_{i,t,h,1}\}_{t,h}$} with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i^B$, \textcolor{red}{where the test uses moving block bootstrap   with $B$ and $\gamma$.}\\
  }

@@

\textcolor{red}{Regarding the hyper-parameters, in this data example, we set $T_i- T_i^* = 30$ and $K = 30$. Note that $K = 30$ is a sensible  training sample size, see discussions for example in  \cite{lin2021minimizing}. Also, $T_i-T_i^*-H$ corresponds to the post-shock time length that analysts are interested in predicting whether the impact of the shock persists.  We set $T_i- T_i^* = 30$  in order to make the post-shock time length moderately large and also for illustration purpose. For sensitivity analysis, we implemented the analysis for different  $H= 2, 4, 6, 8$.}

\textcolor{red}{We summarize our numerical results in Table \ref{coptable}. In the Table \ref{coptable}, $p_1$ stands for the forecast comparison test of \cite{quaedvlieg2021multi} applied for adjusted and unadjusted forecasts on the time series of interest. Note that in practice, it cannot be computed because  $y_{1, t}$ for $t > T_1^*$ is not observed. It is provided   for retrospective  analysis. Second, $\hat{p}_1$ is the  estimate for $p_1$ using $\mbf{W}^*$.  We recorded the voting and weighted voting results in the form of indicators with one being voting for persistence and zero for transience. See the methodological details for $\hat{p}_1$, voting, and weighted voting in Section \ref{sec:multhor}. In companion with the voting, the correctness of the voting is evaluated and provided  in the brackets. For example, ``0 (Yes)'' implies  that the procedure votes for transience and this decision is correct whereas ``1 (No)'' votes for persistence and it is incorrect.  }

@@

\textcolor{red}{Next, we discuss our numerical results.} Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$. It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second. As pointed out by \cite{lin2021minimizing} in Section 5.1(3), the shocks experienced by the first and  third donor are related to recessions, and oil supply shock, respectively. The results are intuitive in the sense that from a retrospective perspective of a data analyst, the shock experienced by the series $\{y_{1,t}\colon t = 1, \ldots, T_1\}$ is due to oil supply shock and recessions caused by COVID-19 pandemic.

Let $a_i^1$ and $a_i^2$ denote the AICs of $\mc{M}_0$ and $\mc{M}$ for $i$th time series, respectively. \textcolor{red}{Based on \ref{model-gen}, which describes $\mc{M}$ and the description of $\mc{M}$ in the beginning of Section \ref{sec::ne}, it may be inferred that $\mc{M}$ captures the post-shock dynamic change whereas $\mc{M}_0$ suggests a persistent post-shock additive location shift.} Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, \textcolor{red}{it turns out that $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=1 >0.5$. Using this aggregated model selection approach, we prefer $\mc{M}$ over $\mc{M}_0$.}

\textcolor{red}{From Table \ref{coptable}, we can see that $p_1$ for $\mc{M}$ is not sensitive to the changes of $H$ and is uniformly 1. Under any reasonable significance level, based on the features of $\mc{M}$, we infer that post-shock dynamics do not differ from the pre-shock one and the shock is not persistent. In contrast, $p_1$ of $\mc{M}_0$ equals 1 for $H = 2$ whereas equals 0 for $H = 4, 6, 8$. It is possible that $\mc{M}_0$ does not fit the data well. In practice, a simple additive post-shock location-shift is rare and more complicated structures cannot be explained using this. To support this claim, we plotted $\{y_{1,t} \colon 1, \ldots, T_1\}$ in Figure \ref{copshocktransience}.}

>>>>

The core idea of our methodology is to first form a donor pool of time series that have undergone similar shocks, then perform the multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi}  with respect to each of these donors to determine whether the shock is prevalent or transient, and then aggregate the decisions from the donors to make a final decision of transience or prevalence for the time series under study for which no post-shock observations are observed. The multi-horizon forecast testing procedure of \cite{quaedvlieg2021multi} is a natural  extension of \cite{diebold1995comparing}. The post-shock setting follows similar logic as that in \cite{lin2021minimizing}.
%Our testing method embraces ideas from forecast aggregation in the post-shock setting \citep{lin2021minimizing}, forecast comparison \citep{diebold1995comparing, quaedvlieg2021multi}, and p-value combination. 
Our procedure has conceptual similarities with 
conditional forecasting \citep{baumeister2014real, kilian2017structural}, 
time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, 
forecasting with judgement and models \citep{svensson2005monetary, monti2008forecast}, 
synthetic control methodology \citep{abadie2010synthetic}, 
synthetic interventions \citep{agarwal2020synthetic, agarwal2020two}, 
and expectation shocks \citep{croushore2006data, baumeister2014general, clements2019measuring}. The synthetic intervention approach in \cite{agarwal2020two} is particularly relevant to our method. These authors construct a panel of countries undergoing a variety of interventions and use it to estimate what COVID case trajectories for a particular country would have looked like under different chosen courses of action. They then demonstrate that the method well replicates the observed trajectories of countries under the chosen intervention. This method works well because there are multiple countries undergoing similar interventions in response to a common shock which occurs at a similar past time for each country. In our setting, we do not specify that the time series in the donor pool be temporally similar to the time series under study, but we require that the shocks to those time series be similar to the shock of the time series under study. In \cite{lin2021minimizing} this similarity was stated in the form of a shock-effect distribution. In the present work, we parameterize similarity into post-shock dynamics for an autoregressive process.

As alluded to above, the success of our approach hinges on the construction of a suitable donor pool that possess similar post-shock dynamics to the time series under study. We develop a pragmatic parametric time series model which parameterizes such a structure. Without such a parameterization there is no avenue for connecting decisions made regarding the post-shock information in the donor pool with the yet-to-be observed post-shock information corresponding to the time series under study. The parameterization that we use states that the post-shock dynamics are determined in part by observed covariates collected right before the first post-shock response is observed. %Such a parameterization will not be known in practice. That being said, one can demonstrate the effectiveness and appropriateness of such a parameterization via a leave one out cross validation approach applied to the donor pool in which all post-shock information is observed \textcolor{red}{need LOOCV approach}. A similar prospective approach was discussed in \cite{lin2021minimizing}. 
We demonstrate the utility of our prevalence testing approach on two real data examples forecasting daily Conoco Phillips stock prices and monthly employment data as well as several simulation examples. Our simulation examples show settings in which our method is expected to work well and demonstrate that the appropriateness of the method decreases as the parametric specifications break down. In the real data examples, we show that the decisions obtained from the donor pool match those that would be observed in the future.

@@

In this section we discuss the background of the multi-horizon forecasting procedure \citep{quaedvlieg2021multi} that is necessary for the investigation of shock behavior in our anticipated post-shock setting. The initial building blocks in the assessment of predictive ability of forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ will make use of a loss differential
$$
  \dbf_{i,t} =  \Llet_{i,t,2} - \Llet_{i,t,1},
$$
where $\Llet_{i,t,j} \in \R^H$ has elements $L^h(y_{i,t}$, $\hat y_{i,t}^{j,h})$, $j = 1,2$, and $L$ is a loss function. Define the expected loss differential as  $E(\dbf_{i,t}) = \mbf\mu_{i,t}$ and let the average expected loss differential be defined as $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
%Hypothesis tests in \cite{quaedvlieg2021multi} are then constructed with respect to estimates of the expected loss differentials $E(\dbf_{i,t}) = \mbf\mu_{i,t}$, %Conditions for these tests require conditions of \cite{giacomini2006tests}. 
%where specific interest is in the average expected loss differential $\mathbf{\mu}_i = \lim_{T\to\infty}\frac{1}{T}\sum_{i=1}^T \mathbf{\mu}_{i,t}$.
%%%\vspace*{0.5cm}\noindent\textbf{Note}: We need more formality for constructing $\hat y^{1,h}_{1,t}$. We could use the forecasts in \cite{lin2021minimizing} and then consider $h$-ahead methods after adjusting for the shock. Or we could consider aggregation approaches which average all post-shock responses of the series in the donor pool. 
%%%\vspace*{0.5cm}
We will then judge forecasts $\hat y^{1,h}_{i,t}$ and $\hat y^{2,h}_{i,t}$ based on the average superior predictive ability (aSPA) \citep{quaedvlieg2021multi}. The aSPA investigates forecast comparisons based on their weighted average loss difference
$$
  \mu^{(\text{Avg})}_i = \textbf{w}_i'\mathbf{\mu}_i = \sum_{h=1}^H w_{i,h} \mu_i^h,
$$
with weights $\textbf{w}_i$ that sum to one. Note that aSPA requires the user to take a stand on the relative importance of under-performance at one horizon against out-performance at another, and note that it is likely that $\mu_i^h > 0$ for $h$ closer to 1 since the user expects that a structural shock will occur and the structural shock is taken into account by forecast 1. With this caveat in mind we will use $w_{i,h} = 1/H$, and we will consider different time horizons $H$ in some of our examples.

Define $\mbf{D}_i = (\mbf{d}_{i, T^*_i+H+1}', \ldots, \mbf{d}_{i, T_i}')$, which is the loss differential matrix of $i$th time series. Note that $\mbf{D}_i$ is of dimension $T_i-T^*_i - H$.   $\mbf{D}_i$ compares $h$-step forecasts of $y_{i, t}$ for $t = T^* + H + 1$ to $t = T$ and $h= 1, \ldots, H$. In this design, adjusted and unadjusted forecasts are different with probability one such that elements of $\mbf{D}_i$ are different from zero with probability one. This prevents excessive zeroes to affect our inference results if $t = H+K +1,  \ldots, T$, where $K$ is the training sample size for parameter estimation of $h$-step forecasts.

@@

%We now demonstrate that computing p-values corresponding to the hypothesis test \eqref{test} using the moving block bootstrap (MBB) is a good approximation.
Let $l = o(T^{1/2})$ be the block length of the MBB where we assume that $T_i = lU_i$. Let $I_1$,\ldots,$I_{K_i}$ be iid random variables uniformly distributed on $\{1,\ldots,T_i-l+1\}$, and define the array 
$$
  \tau_{T_i} = \{I_1+1, \ldots, I_1+l, \ldots, I_{K_i}+1, \ldots, I_{K_i}+l\}.
$$
The pseudo time-series is therefore $\textbf{d}^b_{i,t} = \textbf{d}^b_{i,\tau_{T_i}}$, with elements $d^{hb}_{i,t}$.

\begin{equation} \label{whb}
	\left(\hat{\omega}_{i}^{hb}\right)^2 = \frac{1}{U_i}\sum_{k=1}^{U_i}\left[\frac{1}{l}\left(\sum_{t=1}^l d^{hb}_{i,(k-1)l + t} - \bar{d}^{hb}_{i}\right)^2\right],
\end{equation}
where $\bar{d}^{hb}_{i} = \frac{1}{T_i}\sum_{t=1}^{T_i} d^{hb}_{i,t}$. From the conditions of Theorem 1 and Corollary 1 in \cite{quaedvlieg2021multi}  we have 
\begin{equation} \label{boott}
  \sup_{z\in\R}\Big\vert \Prob^b\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}^b_{i} - \textbf{w}_i'\bar{\dbf}_{i} }{\hat{\zeta}^b_{i}}\right] 
  - \Prob\left[\sqrt{T_i}\frac{\textbf{w}_i'\bar{\dbf}_{i} -  \textbf{w}_i'\mbf{\mu}_{i}}{\hat{\zeta}^b_{i}}\right]
  \Big\vert \overset{P}{\longrightarrow} 0,
\end{equation}
as $T_i\to\infty$ where $l=l_{T_i}=o(\sqrt{T_i})$. We can compute a bootstrap $p$-value as 
\begin{equation} \label{bootp}
  \hat{p}_i^B = \frac{1}{B}\sum_{b=1}^B 1\{t_{i,\text{aSPA}} < t^b_{i,\text{aSPA}}\}. 
\end{equation}
The results \eqref{boott} implies that 
$$
  |\hat p_i^B - \hat p_i| \overset{P}{\to} 0, \quad \text{as} \quad T_i,B \to \infty, 
$$
where $\hat p_i = \Prob(t_{i,\alpha} < t_{i,\text{aSPA}})$ and $t_{i,\alpha}$ is a critical value corresponding to the distribution of $t_{i,\text{aSPA}}$. Therefore bootstrap inference in the donor pool is a good approximation. %We now consider how bootstrap inference in the donor pool is used to test whether a shock is prevalent or transient for the time series under study.

@@

The first approach is a weighted average of the p-values computed in the donor pool which are calculated as in Section \ref{sec:multhor}. The weights reflect the similarity between $\x_{i,T^*_i+1}$ and $\x_{1,T^*_1+1}$, and are similar to the weights computed in \cite{lin2021minimizing}. We now discuss the details. Let
\begin{align*}
	\bs{X}= \begin{pmatrix}
		\bs{x}_{2, T_2^*+1}'  \\
		\vdots   \\
		\bs{x}_{n+1, T_{n+1}^*+1}' 
	\end{pmatrix}.
\end{align*}
In this paper, we consider this simple form of $\bs{X}$ for illustrative purpose. However,  more general $\bs{X}$'s are allowable. For example, $\bs{X}$ can also include $\bs{x}_{i, T_i^*-j+1}$ for $j = 2, \ldots, q_2$, which considers the lagged covariates in the dynamic model \eqref{model-gen}. Let $\bs{X}^*$ be the same as $\bs{X}$ with each column scaled to have mean 0 and standard deviation 1. We compute the weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}. Note that the modeling part for the response $y_{i,t}$ does not necessarily involve scaled covariates. From this construction we obtain the weighted average p-value 
\begin{equation} \label{wpval}
 \hat{p}_1 = \sum_{i=2}^{n+1} w_i^* \hat{p}_i^B,	
\end{equation}
where $\hat{p}_i^B$ is given as \eqref{bootp} and $w_i^*$ is the weight corresponding to the similarity between the first and $(i+1)$th row of $\mbf{X}^*$.

\textcolor{red}{Need to make a decision about voting and weighted voting; not sure if it is more robust or efficient than the weighted p-value approach. If it is not superior than the weighted approach in any way then we should remove it.} We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool. Given a significance level $\alpha$ and estimates $\{\hat{p}_i^B \colon i = 2, \ldots, n+1\}$, we compute the vote
\begin{align*}
	V = I\Big\{\frac{1}{n} \sum_{i=2}^{n+1} I (\hat{p}_i^B\leq \alpha) \geq 0.5\Big\},
\end{align*}
where $I(\cdot)$ is an indicator function. The idea of voting is very intuitive in the sense that donors vote for the shock persistence or transience  using a hypothesis testing approach and the one receiving more votes is returned.  Second, the weighted voting generalizes this idea by making using of  the similarity weights $\mbf{W}^*$. It is defined as 
\begin{align*}
	V^* = I\Big\{ \sum_{i=2}^{n+1} w_i^* I (\hat{p}_i^B\leq \alpha) \geq 0.5\Big\}.
\end{align*}

Algorithm \ref{Bu} describes the mechanics of computing $\mbf{W}^*, \hat{p}_1, V, V^*$ in more detail. There are a couple of details that are worth noting. First, for $t = T_i+1$ and $i \geq 2$, we used to the methodology of \cite{lin2021minimizing} to compute point forecast for $\hat{y}_{i,t}^{2,h}$. Note that for $t = T_i+1$, using ordinary least square conditional forecast yields $\hat{y}_{i,t}^{2,h}=  \hat{y}_{i,t}^{1,h}$ as those two forecast just differ by shock information, which is not available at this time point. We make such adjustment for the reason that  the method of  \cite{lin2021minimizing} is generally more likely to perform better than the ordinary forecast under certain conditions. Second, notice that we evaluate forecast comparison for $t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$ with time length smaller than $T_i$. It is because the framework of \cite{quaedvlieg2021multi} needs training sample, which implicitly requires users to feed the algorithm with moderately large dataset for a more credible analysis.

@@

 		\If{$t-h = T_i^*$, $i\geq 3$, and $h =1$}{
 		$\hat{y}_{i,t}^{2, h}= \hat{y}_{i,t}^{2, h} + \hat{\alpha}_{\rm wadj}$
 		}
 		Compute the squared error loss $l_{i,t,h, 1}$ based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{1, h}$\\
 		 Compute the squared error loss $l_{i,t,h, 2}$ based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{2, h}$
 		}
 	}
 	Construct the loss differential matrix   with element $l_{i,t,h, 2}-l_{i,t,h, 1}$ at $t$th row and $h$th column \\
 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix $\{l_{i,t,h,2}-l_{i,t,h,1}\}_{t,h}$ with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i^B$, where the test uses moving block bootstrap   with $B$ and $\gamma$.\\
  }

@@

In this data example we set $T_i- T_i^* = 30$ and $K = 30$. Note that $K = 30$ is a sensible  training sample size, see discussions for example in  \cite{lin2021minimizing}. The quantity $T_i-T_i^*-H$ corresponds to the post-shock time length that analysts are interested in predicting whether the impact of the shock persists.  We set $T_i- T_i^* = 30$  in order to make the post-shock time length moderately large and also for illustration purpose. For sensitivity analysis, we implemented the analysis for different  $H= 2, 4, 6, 8$.

We summarize our numerical results in Table \ref{coptable}. In the Table \ref{coptable}, $p_1$ stands for the forecast comparison test of \cite{quaedvlieg2021multi} applied for adjusted and unadjusted forecasts on the time series of interest. Note that in practice, it cannot be computed because  $y_{1, t}$ for $t > T_1^*$ is not observed. It is provided   for retrospective  analysis. Second, $\hat{p}_1$ is the  estimate for $p_1$ using $\mbf{W}^*$.  We recorded the voting and weighted voting results in the form of indicators with one being voting for persistence and zero for transience. See the methodological details for $\hat{p}_1$, voting, and weighted voting in Section \ref{sec:multhor}. In companion with the voting, the correctness of the voting is evaluated and provided  in the brackets. For example, ``0 (Yes)'' implies  that the procedure votes for transience and this decision is correct whereas ``1 (No)'' votes for persistence and it is incorrect.

@@

We now discuss the numerical results. Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$. It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second. As pointed out by \cite{lin2021minimizing} in Section 5.1(3), the shocks experienced by the first and  third donor are related to recessions, and oil supply shock, respectively. The results are intuitive in the sense that from a retrospective perspective of a data analyst, the shock experienced by the series $\{y_{1,t}\colon t = 1, \ldots, T_1\}$ is due to oil supply shock and recessions caused by COVID-19 pandemic.

Let $a_i^1$ and $a_i^2$ denote the AICs of $\mc{M}_0$ and $\mc{M}$ for $i$th time series, respectively. Based on \eqref{model-gen}, which describes $\mc{M}$ and the description of $\mc{M}$ in the beginning of Section \ref{sec::ne}, it may be inferred that $\mc{M}$ captures the post-shock dynamic change whereas $\mc{M}_0$ suggests a persistent post-shock additive location shift. Using the synthetic pairwise model selection procedures specified in Corollary \ref{coro2}, it turns out that $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)=1 >0.5$. Using this aggregated model selection approach, we prefer $\mc{M}$ over $\mc{M}_0$. \textcolor{red}{Add column for AIC results}

From Table \ref{coptable}, we can see that $p_1$ for $\mc{M}$ is not sensitive to the changes of $H$ and is uniformly 1. Under any reasonable significance level, based on the features of $\mc{M}$, we infer that post-shock dynamics do not differ from the pre-shock one and the shock is not persistent. In contrast, $p_1$ of $\mc{M}_0$ equals 1 for $H = 2$ whereas equals 0 for $H = 4, 6, 8$. It is possible that $\mc{M}_0$ does not fit the data well. In practice, a simple additive post-shock location-shift is rare and more complicated structures cannot be explained using this. To support this claim, we plotted $\{y_{1,t} \colon 1, \ldots, T_1\}$ in Figure \ref{copshocktransience}.
